---
title: "HW3 Kariya CSSS569"
author: "Hitomi Kariya, MPH in Health Services"
date: "3/17/2020"
output: html_notebook
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

```{r}
## Load libraries ##
library(shiny)          # Shiny web app
library(shinydashboard) # ShinyDashboard
library(plotly)         # Interactive plotly map/BI
library(tidyverse)         # Load CSV data sets
```

* I have created a dashboard of two maps for the number of cases and deaths caused by coronavirus in the United States. You can hover over the maps to see the number of cases and deaths reported by states.

* Underlying data: The data is retreived from https://www.worldometers.info/coronavirus/country/us/ .

```{r}
## Data assigning & object preps ##
# Load a dataset
df <- read_csv("covid19_map_state.csv")

# Create map layers/tool tips
df$hover <- with(df, paste(state_full, '<br>'))

## Plotly_Map this data: l, g, p arguments.##
# Give state light white boundaries with `l` ojbect
l <- list(color = "White", width = 0.5)

# Specify some map options with `g` object
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white'))

# Create a plotting map object with `p` object for cases
p <- plot_geo(df, locationmode = 'USA-states') %>%
  add_trace(
    z = ~cases, text = ~hover, locations = ~state, marker = list (line=l),
    color = ~cases, colors = 'Blues'
  ) %>%
  colorbar(title = "Number of Cases") %>%
  layout(
    title = 'Confirmed Cases by State<br>(As of July 8, 2020)',
    geo = g
  )

# Create a plotting map object with `p2` object for deaths
p2 <- plot_geo(df, locationmode = 'USA-states') %>%
  add_trace(
    z = ~deaths, text = ~hover, locations = ~state, marker = list (line=l),
    color = ~cases, colors = 'Reds'
  ) %>%
  colorbar(title = "Number of Deaths") %>%
  layout(
    title = 'Confirmed Deaths by State<br>(As of July 8, 2020)',
    geo = g
  )

# Assign the dataset to global environment
assign("df", df, envir=globalenv())
```


```{r}
## ui.R: All about header, sidebar, and body ##
# Create a Header
header <- dashboardHeader(title = "COVID-19 in U.S.")

# Create a Sidebar
sidebar <- dashboardSidebar(
    sidebarMenu(
      menuItem("Map by Cases", tabName = "dashboard", icon = icon("th")),
      menuItem("Map by Deaths", tabName = "widgets", icon = icon("th"))
      ))
  

# Create a Body
body <- dashboardBody(
  tabItems(
    #First tab content
    tabItem(tabName = "dashboard",
      fluidRow(
        box(
          title = "How many COVID-19 cases are reported in the United States?",
          width = 4,
          status = "primary", 'This is a map for the number of cases reported to be caused by coronavirus in the United States. The data was retreived on July 8, 2020. New York state has reported the most number of confirmed cases.'
          ),
        box(
          title = "COVID-19 in the United States", p, width = 8
        )
      )
    ),
    #Second tab content
    tabItem(tabName = "widgets",
      fluidRow(
        box(
          title = "How many COVID-19 deaths are reported in the United States?",
          width = 4,
          status = "primary", 'This is a map for the number deaths reported to be caused by coronavirus in the United States. The data was retreived on July 8, 2020.'
          ),
        box(
          title = "COVID-19 in the United States", p2, width = 8
        )
      )
        )
    )
)

# Assign everything to UI
ui <- dashboardPage(header, sidebar, body, skin = "purple")

## server.R ##
server <- function(input, output) {}

## Creating the final product ##
shinyApp(ui, server)
```

* Next step 1: Figure out how to display these two maps as one map
* Next step 2: Figure out how to render it as a html file 
* Next step 3: Figure out a way to click on each state and display the numbers on the right bottom corner as a box.
* Next step 4: Figure out a way to click on each state, then details on funding type can be displayed on the right bottom corner as a box.

*References
https://plotly-r.com/maps.html
